---
title: "All Time Points"
author: "Shaun Stearns"
date: "9/26/2019"
output: 
  word_document: 
    fig_height: 7
    fig_width: 7
---

```{r}
library(DescTools)
library(haven)
library(tidyverse)
library(lubridate)
library(plyr)
library(norm2)
library(norm)

library(rpart)
library(rpart.plot)
library(caret)
library(randomForest)
library(adabag)
library(jtools)
library(sandwich)
library(rattle)
library(gbm)
library(doSNOW)
library(foreach)
library(ggplot2)
library(rfUtilities)
library(party)

library("cluster")
library("factoextra")
library("magrittr")
library("factoextra")
```


# Multiple Regression 1
## Lowest Weigh-in
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(10,4,7,15,16,17:53)]
DF.t <- DF.t[c(1,7:42)]
DF.t = scale(DF.t, center = TRUE, scale = TRUE)
DF.t <- as.data.frame(DF.t)
reg <- lm(Lowestweighinkg ~., DF.t)
```

```{r, echo=FALSE}
summ(reg, part.corr = TRUE, confint = TRUE, coeftable = TRUE)
```

```{r, echo=FALSE}
plot_summs(reg, ci_level = .95, exp = TRUE, robust = TRUE)
```


# Regression Tree 1
```{r}

DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(10,4,7,15,16,17:53)]
DF.t <- DF.t[c(1,7:42)]
model <- train(
  Lowestweighinkg ~., DF.t, method = "ctree",
  trControl = trainControl("cv", number = 10),
  tuneGrid = expand.grid(mincriterion = 0.95)
)
model$results
```

## Tree Plot
```{r model$finalModel, echo=FALSE}
plot(model$finalModel, type = "simple")
```




# Random Forest 1
```{r}

DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(10,4,7,15,16,17:53)]
DF.t <- DF.t[c(1,7:42)]
rf <- randomForest(Lowestweighinkg ~ ., data = DF.t, ntree = 25,
                   mtry = 4, nodesize = 5, importance = TRUE)
```

## Signicance Testing
```{r}
rf.perm <- rf.significance(rf, DF.t, q = 0.99, p = 0.05, nperm=99, ntree=25)
rf.perm
```

## Variable Importance Plot
```{r}
varImpPlot(rf, type = 1, main = "Lowest Rec Weight")
```




# Multiple Regression 2
## Difference Between First Weigh-in and Lowest Weigh-in
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(11,4,7,15,16,17:53)]
DF.t <- DF.t[c(1,7:42)]
DF.t = scale(DF.t, center = TRUE, scale = TRUE)
DF.t <- as.data.frame(DF.t)
reg <- lm(AbsDiffFirstWeighinkg ~., DF.t)
```

```{r, echo=FALSE}
summ(reg, part.corr = TRUE, confint = TRUE, coeftable = TRUE)
```

```{r, echo=FALSE}
plot_summs(reg, ci_level = .95, exp = TRUE, robust = TRUE)
```



# Regression Tree 2
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(11,4,7,15,16,17:53)]
DF.t <- DF.t[c(1,7:42)]
model <- train(
  AbsDiffFirstWeighinkg ~., DF.t, method = "ctree",
  trControl = trainControl("cv", number = 10),
  tuneGrid = expand.grid(mincriterion = 0.95)
)
model$results
```

## Tree Plot
```{r}
plot(model$finalModel, type = "simple")
```



# Random Forest 2
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(11,4,7,15,16,17:53)]
DF.t <- DF.t[c(1,7:42)]
rf <- randomForest(AbsDiffFirstWeighinkg ~ ., data = DF.t, ntree = 25,
                   mtry = 4, nodesize = 5, importance = TRUE)
```

## Signicance Testing
```{r}
rf.perm <- rf.significance(rf, DF.t, q = 0.99, p = 0.05, nperm=99, ntree=25)
rf.perm
```

## Variable Importance Plot
```{r}
varImpPlot(rf, type = 1, main = "Absolute Diff Weight (1st)")
```




# Multiple Regression 3
## Differnece Between Initial Weigh-in and Lowest Weigh-in
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(12,4,7,15,16,17:53)]
DF.t <- DF.t[c(1,7:42)]
DF.t = scale(DF.t, center = TRUE, scale = TRUE)
DF.t <- as.data.frame(DF.t)
reg <- lm(AbsDiffInitWeighinkg ~., DF.t)
```

```{r, echo=FALSE}
summ(reg, part.corr = TRUE, confint = TRUE, coeftable = TRUE)
```

```{r, echo=FALSE}
plot_summs(reg, ci_level = .95, exp = TRUE, robust = TRUE)
```



# Regression Tree 3
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(12,4,7,15,16,17:53)]
DF.t <- DF.t[c(1,7:42)]
model <- train(
  AbsDiffInitWeighinkg ~., DF.t, method = "ctree",
  trControl = trainControl("cv", number = 10),
  tuneGrid = expand.grid(mincriterion = 0.95)
)
model$results
```

## Tree Model
```{r}
plot(model$finalModel, type = "simple")
```


# Random Forest 3
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(12,4,7,15,16,17:53)]
DF.t <- DF.t[c(1,7:42)]
rf <- randomForest(AbsDiffInitWeighinkg ~ ., data = DF.t, ntree = 25,
                   mtry = 4, nodesize = 5, importance = TRUE)
```

## Signicance Testing
```{r}
rf.perm <- rf.significance(rf, DF.t, q = 0.99, p = 0.05, nperm=99, ntree=25)
rf.perm
```

## Variable Importance Plot
```{r}
varImpPlot(rf, type = 1, main = "Absolute Diff Weight (Init)")
```





# Multiple Regression 4
## Curriculum Week (or Length of Time with DF?)
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(4,7,15,16,17:53)]
DF.t <- DF.t[c(5,6:41)]
DF.t = scale(DF.t, center = TRUE, scale = TRUE)
DF.t <- as.data.frame(DF.t)
reg <- lm(CurriculumWeek ~., DF.t)
```

```{r, echo=FALSE}
summ(reg, part.corr = TRUE, confint = TRUE, coeftable = TRUE)
```

```{r, echo=FALSE}
plot_summs(reg, ci_level = .95, exp = TRUE, robust = TRUE)
```



# Regression Tree 4
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(4,7,15,16,17:53)]
DF.t <- DF.t[c(5,6:41)]
model <- train(
  CurriculumWeek ~., DF.t, method = "ctree",
  trControl = trainControl("cv", number = 10),
  tuneGrid = expand.grid(mincriterion = 0.95)
)
model$results
```

## Tree Model
```{r}
plot(model$finalModel, type = "simple")
```



# Random Forest 4
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(4,7,15,16,17:53)]
DF.t <- DF.t[c(5,6:41)]
rf <- randomForest(CurriculumWeek ~ ., data = DF.t, ntree = 25,
                   mtry = 4, nodesize = 5, importance = TRUE)
```

## Signicance Testing
```{r}
rf.perm <- rf.significance(rf, DF.t, q = 0.99, p = 0.05, nperm=99, ntree=25)
rf.perm
```

## Variable Importance Plot
```{r}
varImpPlot(rf, type = 1, main = "Goal Weight")
```




# Multiple Regression 5
## Differnce in BMI
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(14,4,7,15,16,17:53)]
DF.t <- DF.t[c(1,7:42)]
DF.t = scale(DF.t, center = TRUE, scale = TRUE)
DF.t <- as.data.frame(DF.t)
reg <- lm(BMIDifference ~., DF.t)
```

```{r, echo=FALSE}
summ(reg, part.corr = TRUE, confint = TRUE, coeftable = TRUE)
```

```{r, echo=FALSE}
plot_summs(reg, ci_level = .95, exp = TRUE, robust = TRUE)
```



# Regression Tree 5
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(14,4,7,15,16,17:53)]
DF.t <- DF.t[c(1,7:42)]
model <- train(
  BMIDifference ~., DF.t, method = "ctree",
  trControl = trainControl("cv", number = 10),
  tuneGrid = expand.grid(mincriterion = 0.95)
)
model$results
```

## Tree Model
```{r}
plot(model$finalModel, type = "simple")
```



# Random Forest 5
```{r}
DF <- read.csv("C:/Users/LaoTz/Desktop/DF Articles/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(14,4,7,15,16,17:53)]
DF.t <- DF.t[c(1,7:42)]
rf <- randomForest(BMIDifference ~ ., data = DF.t, ntree = 25,
                   mtry = 4, nodesize = 5, importance = TRUE)
```

## Signicance Testing
```{r}
rf.perm <- rf.significance(rf, DF.t, q = 0.99, p = 0.05, nperm=99, ntree=25)
rf.perm
```

## Variable Importance Plot
```{r}
varImpPlot(rf, type = 1, main = "BMI Diff")
```

