---
title: "Weight Loss Week 16"
author: "Shaun Stearns"
date: "1/28/2021"
output: html_document
---

```{r}
library(DescTools)
library(haven)
library(tidyverse)
library(lubridate)
library(plyr)
library(norm2)
library(norm)

library(rpart)
library(rpart.plot)
library(caret)
library(randomForest)
library(adabag)
library(jtools)
library(sandwich)
library(rattle)
library(gbm)
library(doSNOW)
library(foreach)
library(ggplot2)
library(rfUtilities)
library(party)

library("cluster")
library("factoextra")
library("magrittr")
library("factoextra")
```

# Multiple Regression 1
## Lowest Weigh-in
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(10,18,21,24,27,30,33,36,39,42,45,48,51)]
DF.t = scale(DF.t, center = TRUE, scale = TRUE)
DF.t <- as.data.frame(DF.t)
reg <- lm(Lowestweighinkg ~., DF.t)
summ(reg, part.corr = TRUE, confint = TRUE, coeftable = TRUE)

plot_summs(reg, ci_level = .95, exp = TRUE, robust = TRUE)
```

# Regression Tree 1
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(10,18,21,24,27,30,33,36,39,42,45,48,51)]
model <- train(
  Lowestweighinkg ~., DF.t, method = "ctree",
  trControl = trainControl("cv", number = 10),
  tuneGrid = expand.grid(mincriterion = 0.95)
)
model$results
## Tree Model
plot(model$finalModel, type = "simple")
```

# Random Forest 1
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(10,18,21,24,27,30,33,36,39,42,45,48,51)]
rf <- randomForest(Lowestweighinkg ~ ., data = DF.t, ntree = 25,
                   mtry = 4, nodesize = 5, importance = TRUE)
## Signicance Testing
rf.perm <- rf.significance(rf, DF.t, q = 0.99, p = 0.05, nperm=99, ntree=25)
rf.perm
## Variable Importance Plot
varImpPlot(rf, type = 1, main = "Lowest Rec Weight")
```



# Multiple Regression 2
## Difference Between First Weigh-in and Lowest Weigh-in
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(11,18,21,24,27,30,33,36,39,42,45,48,51)]
DF.t = scale(DF.t, center = TRUE, scale = TRUE)
DF.t <- as.data.frame(DF.t)
reg <- lm(AbsDiffFirstWeighinkg ~., DF.t)
summ(reg, part.corr = TRUE, confint = TRUE, coeftable = TRUE)

plot_summs(reg, ci_level = .95, exp = TRUE, robust = TRUE)
```


# Regression Tree 2
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(11,18,21,24,27,30,33,36,39,42,45,48,51)]
model <- train(
  AbsDiffFirstWeighinkg ~., DF.t, method = "ctree",
  trControl = trainControl("cv", number = 10),
  tuneGrid = expand.grid(mincriterion = 0.95)
)
model$results
## Tree Model
plot(model$finalModel, type = "simple")
```

# Random Forest 2
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(11,18,21,24,27,30,33,36,39,42,45,48,51)]
rf <- randomForest(AbsDiffFirstWeighinkg ~ ., data = DF.t, ntree = 25,
                   mtry = 4, nodesize = 5, importance = TRUE)
## Signicance Testing
rf.perm <- rf.significance(rf, DF.t, q = 0.99, p = 0.05, nperm=99, ntree=25)
rf.perm
## Variable Importance Plot
varImpPlot(rf, type = 1, main = "Absolute Diff Weight (1st)")
```



# Multiple Regression 3
## Differnece Between Initial Weigh-in and Lowest Weigh-in
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(12,18,21,24,27,30,33,36,39,42,45,48,51)]
DF.t = scale(DF.t, center = TRUE, scale = TRUE)
DF.t <- as.data.frame(DF.t)
reg <- lm(AbsDiffInitWeighinkg ~., DF.t)
summ(reg, part.corr = TRUE, confint = TRUE, coeftable = TRUE)

plot_summs(reg, ci_level = .95, exp = TRUE, robust = TRUE)
```

# Regression Tree 3
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(12,18,21,24,27,30,33,36,39,42,45,48,51)]
model <- train(
  AbsDiffInitWeighinkg ~., DF.t, method = "ctree",
  trControl = trainControl("cv", number = 10),
  tuneGrid = expand.grid(mincriterion = 0.95)
)
model$results
## Tree Model
plot(model$finalModel, type = "simple")
```

# Random Forest 3
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(12,18,21,24,27,30,33,36,39,42,45,48,51)]
rf <- randomForest(AbsDiffInitWeighinkg ~ ., data = DF.t, ntree = 25,
                   mtry = 4, nodesize = 5, importance = TRUE)
## Signicance Testing
rf.perm <- rf.significance(rf, DF.t, q = 0.99, p = 0.05, nperm=99, ntree=25)
rf.perm
## Variable Importance Plot
varImpPlot(rf, type = 1, main = "Absolute Diff Weight (Init)")
```




# Multiple Regression 4
## Curriculum Week (or Length of Time with DF?)
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(17,18,21,24,27,30,33,36,39,42,45,48,51)]
DF.t = scale(DF.t, center = TRUE, scale = TRUE)
DF.t <- as.data.frame(DF.t)
reg <- lm(CurriculumWeek ~., DF.t)
summ(reg, part.corr = TRUE, confint = TRUE, coeftable = TRUE)

plot_summs(reg, ci_level = .95, exp = TRUE, robust = TRUE)
```

# Regression Tree 4
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(17,18,21,24,27,30,33,36,39,42,45,48,51)]
model <- train(
  CurriculumWeek ~., DF.t, method = "ctree",
  trControl = trainControl("cv", number = 10),
  tuneGrid = expand.grid(mincriterion = 0.95)
)
model$results
## Tree Model
plot(model$finalModel, type = "simple")
```

# Random Forest 4
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(17,18,21,24,27,30,33,36,39,42,45,48,51)]
rf <- randomForest(CurriculumWeek ~ ., data = DF.t, ntree = 25,
                   mtry = 4, nodesize = 5, importance = TRUE)
## Signicance Testing
rf.perm <- rf.significance(rf, DF.t, q = 0.99, p = 0.05, nperm=99, ntree=25)
rf.perm
## Variable Importance Plot
varImpPlot(rf, type = 1, main = "Goal Weight")
```



# Multiple Regression 5
## Differnce in BMI
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(14,18,21,24,27,30,33,36,39,42,45,48,51)]
DF.t = scale(DF.t, center = TRUE, scale = TRUE)
DF.t <- as.data.frame(DF.t)
reg <- lm(BMIDifference ~., DF.t)
summ(reg, part.corr = TRUE, confint = TRUE, coeftable = TRUE)

plot_summs(reg, ci_level = .95, exp = TRUE, robust = TRUE)
```

# Regression Tree 5
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(14,18,21,24,27,30,33,36,39,42,45,48,51)]
model <- train(
  BMIDifference ~., DF.t, method = "ctree",
  trControl = trainControl("cv", number = 10),
  tuneGrid = expand.grid(mincriterion = 0.95)
)
model$results
## Tree Model
plot(model$finalModel, type = "simple")
```

# Random Forest 5
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(14,18,21,24,27,30,33,36,39,42,45,48,51)]
rf <- randomForest(BMIDifference ~ ., data = DF.t, ntree = 25,
                   mtry = 4, nodesize = 5, importance = TRUE)
## Signicance Testing
rf.perm <- rf.significance(rf, DF.t, q = 0.99, p = 0.05, nperm=99, ntree=25)
rf.perm
## Variable Importance Plot
varImpPlot(rf, type = 1, main = "BMI Diff")

t(t(names(DF.t)))
View(DF$AgeCode)
View(DF$AgeinCode)
```




# Logistic Regression 6
## Age and Engagement Predictors
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(6,18,21,24,27,30,33,36,39,42,45,48,51)]
lm.fit <- glm(AgeinCode ~., data = DF.t, family = "binomial")
data.frame(summary(lm.fit)$coefficients, odds = exp(coef(lm.fit))) 
round(data.frame(summary(lm.fit)$coefficients, odds = exp(coef(lm.fit))), 5)

plot_summs(logreg, ci_level = .95, exp = TRUE, robust = TRUE)
```


# ANOVA for Age Category
## Comparison on Weight Loss
```{r}
anova1 <- aov(DF$AbsDiffFirstWeighinkg ~ DF$AgeCode)
summary(anova1, digits = 4)
PostSchf <- ScheffeTest(anova1, conf.level=NA)
PostSchf

anova2 <- aov(DF$AbsDiffInitWeighinkg ~ DF$AgeCode)
summary(anova2, digits = 4)
PostSchf <- ScheffeTest(anova1, conf.level=NA)
PostSchf

anova3 <- aov(DF$BMIDifference ~ DF$AgeCode)
summary(anova3, digits = 4)
PostSchf <- ScheffeTest(anova1, conf.level=NA)
PostSchf
```

# Regression Tree 6
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(6,18,21,24,27,30,33,36,39,42,45,48,51)]
model <- train(
  DF.t$AgeinCode ~., DF.t, method = "ctree",
  trControl = trainControl("cv", number = 10),
  tuneGrid = expand.grid(mincriterion = 0.95)
)
model$results
## Tree Model
plot(model$finalModel, type = "simple")
```

# Random Forest 6
```{r}
DF <- read.csv("D:/DF Analysis/WeightLoss.csv", header = TRUE)
DF <- na.omit(DF)
DF.t <- DF[-c(36,37,56)]
DF.t <- DF.t[c(14,18,21,24,27,30,33,36,39,42,45,48,51)]
rf <- randomForest(BMIDifference ~ ., data = DF.t, ntree = 25,
                   mtry = 4, nodesize = 5, importance = TRUE)
## Significance Testing
rf.perm <- rf.significance(rf, DF.t, q = 0.99, p = 0.05, nperm=99, ntree=25)
rf.perm
## Variable Importance Plot
varImpPlot(rf, type = 1, main = "BMI Diff")
```